\documentclass[12pt,letterpaper]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}

\title{SE 3XA3: Problem Statement}

\author{Group 10 \\ Lab: L03 \\ Aamina Hussain, hussaa54 \\ Jessica Dawson, dawsor1 \\ Fady Morcos, morcof2}
\date{}

\begin{document}
\maketitle


\section{What problem are you trying to solve?}
Art is an important aspect of many people's lives. The ability to quickly generate abstract art for use in both personal and professional contexts can be a great benefit to people. In this case, we need a program that can allow the user to easily generate a unique abstract art image according to their preferences. This program should have multiple options to allow the user to have creative freedom when creating their design.

\section{Why is this an important problem?}
Many people use pieces of art for both personal and job related reasons. For example, a business owner may need an attractive background for their website or to create a poster to advertise their business. An individual may also want to create a nice background for their laptop or wallpaper for their phones. Sometimes, the art portion of a task is not the priority, and using an abstract art generator is a quick and simple way to create something aesthetically pleasing in a short amount of time.

\section{What is the context of the problem you are solving?}
The re-creation of this abstract art generator will affect many people, or stakeholders. These stakeholders include the developers of the program, as well as the clients or users of the program. The developers will develop the program, then provide regular updates and maintenance if necessary. The users will actually use the program after it has been completed. The environment for this software would a desktop computer or laptop, and should run in a Windows, Linux, and Mac OS environment. For this reason, the aforementioned users can be any individual with access to a desktop environment.

\end{document}
